Eclipse Che for Fair and Easy Education

### 2019-05-09 che.tex
removed me, myself and I

\section{Introduction}
\label{sec:Introduction}
As children we, used to look into the clouds and count sheep. 
As developers, we look into the clouds and check our applications.  
Cloud technologies are already state of the art, enabling global players like Google to run applications on a world-scale.
The market-leaders stocked up their portfolios with  a  variety  of  different  cloud  technologies,  ranging from cloud computing, cloud storage, database-as-a-service or rentable authentication. 
Modern software needs to be scalable, self-contained, and should run on any device, as well as in the cloud.  
This trend is also visible in Google searches \ref{fig:digdocker}.

@@

The last component is the Che-administration server. 
In the administration-server the workspaces are orchestrated and monitored. 
The authorization is also done at the admin-server and not by every workspace.
The workspaces can be split amongst multiple machines.
The runtimes do not necessarily need to be on the same machines as their workspaces. 
Instead of the web-based IDE, you can connect a desktop IDE to your workspace. 
This is done by mounting the workspaces-filesystem  in  your  desktop  IDE. 
This  will grant you access to autocompletion and other features, but you will miss Che specific helpers the web-IDE offers. 
My personal oppinion is, that mounting remote file systems for development sounds like a infinite source of problems. 
I expect this feature to be rather a proof of concept.

@@

This is one of the primary goals of the DevOps approach \cite{JA16}. 
The workspace can therefore form totally new ways of programming, such as IoT Applications \footnote{he Plugin Arktik for Eclipse offered IoT Development with Che.While Arktik is unsupported since February 2019, it proved that the concept worked.} or a full setup of micro-services \cite{IV18}, while being agile and reproducible.
\subsection{Sharing Results}
The topic \textit{docker for reproducible research} has already been promoted \cite{BO15} and successfully applied to complex topics \cite{ST16} such as machine learning. 
As Clark et al. \cite{CL14} have used code of the several repositories provided from their university, and I expect most of these projects to be of scientific nature, 50\% of the research results where not reproducible.

@@

In general, this approach enables studies to be less about the subject, but instead to be about learning the subject. 
I consider this the primary goal of university courses. 
Another benefit for education is about fairness in IT-Education.

@@

While this sounds harsh towards companies, I think unbiased education for students is not a nice thing to have, but a core concept of education in general. 
Only if that is true, the students can make unbiased decisions and make unbiased research. 
Being dependent on Google for Universities is in a similar way disturbing, as if a biology faculty would be sponsored by Bayer. 
One can only imagine a grim future if the curriculum is influenced by profit. 
\section*{Future Work}
\label{sec:FutureWork}
As this paper only summarizes benefits and outlines some ideas, the next step would be to put it to the test.
In addition, a study could be elaborated on both the acceptance and effect of a CI/CD based development course with Che. 
Unfortunately, the study would lack any comparison as there are few courses on this topic. 
These studies could be done with universities and corporations, which 
may yield very different results.

>>>>

\section{Introduction}
\label{sec:Introduction}
Children look into the clouds and count sheep. 
Developers look into the clouds and check their applications.  
Cloud technologies are already state of the art, enabling global players like Google to run applications on a world-scale.
The market-leaders stocked up their portfolios with  a  variety  of  different  cloud  technologies,  ranging from cloud computing, cloud storage, database-as-a-service or rentable authentication. 
Modern software needs to be scalable, self-contained, and should run on any device, as well as in the cloud.  
This trend is also visible in Google searches \ref{fig:digdocker}.

@@

The last component is the Che-administration server. 
In the administration-server the workspaces are orchestrated and monitored. 
The authorization is also done at the admin-server and not by every workspace.
The workspaces can be split amongst multiple machines.
The runtimes do not necessarily need to be on the same machines as their workspaces. 
Instead of the web-based IDE, you can connect a desktop IDE to your workspace. 
This is done by mounting the workspaces-filesystem  in  your  desktop  IDE. 
This  will grant you access to autocompletion and other features, but you will miss Che specific helpers the web-IDE offers. 
Mounting remote file systems for development sounds lie an infinite source of problems.
This feature looks to be rather a proof of concept.

@@

This is one of the primary goals of the DevOps approach \cite{JA16}. 
The workspace can therefore form totally new ways of programming, such as IoT Applications \footnote{he Plugin Arktik for Eclipse offered IoT Development with Che.While Arktik is unsupported since February 2019, it proved that the concept worked.} or a full setup of micro-services \cite{IV18}, while being agile and reproducible.
\subsection{Sharing Results}
The topic \textit{docker for reproducible research} has already been promoted \cite{BO15} and successfully applied to complex topics \cite{ST16} such as machine learning. 
As Clark et al. \cite{CL14} have used code of several repositories provided from their university, most of the projects can be expected scientific or experimental, 50\% of the research results were not reproducible.

@@

In general, this approach enables studies to be less about the subject, but instead to be about learning the subject. 
This can be considered one of the primary goals of university courses. 
Another benefit for education is about fairness in IT-Education.

@@

While this sounds harsh towards companies, unbiased education for students is not a nice thing to have, but a core concept of education in general. 
Only if that is true, the students can make unbiased decisions and make unbiased research. 
Being dependent on Google for Universities is in a similar way disturbing, as if a biology faculty would be sponsored by Bayer. 
One can only imagine a grim future if the curriculum is influenced by profit. 
\section*{Future Work}
\label{sec:FutureWork}
As this paper only summarizes benefits and outlines some ideas, the next step would be to put it to the test.
In addition, a study could be elaborated on both the acceptance and effect of a CI/CD based development course with Che. 
Unfortunately, the study would lack any comparison as there are few courses on this topic. 
These studies could be done with universities and corporations, which 
may yield very different results.
